Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/RelatedWork.tex
Draft for the section, formalization of Java8.

\subsection{Formalization of Java8}
We provide a simple formalization for a subset of Java including default/static
interface methods and object initialization literals (often called anonymous
local inner classes).  A similar formalization was drafted by Goetz and
Field~\cite{goetz12fdefenders} to formalize defender (default) methods in
Java. However this formalization is limited to model exactly one method inside
classes/interfaces.\bruno{explain why having multiple methods is significantly
  more challenging.} Our code generation generates several methods that may
interacts with each other and methods defined by user. Thus implementing and
formalizing multiple methods inside interfaces adds complexity greatly.
\marco{I do not see this as a good explanation, I think we may just remove the `one method limitation discussion'. Is their work modelling interactions between abstract and default methods? like making a default method abstract again?}
% As an evidence of the attention and care present in our formalization work,
% while double-checking the behaviour of Java in side cases we have discovered a
% likely bug in the current \texttt{javac}.\marco{refer to before when we explain
%   the issue.}

>>>>

\subsection{Formalization of Java8}
We provide a simple formalization for a subset of Java including default/static
interface methods and object initialization literals (often called anonymous
local inner classes).  A similar formalization was drafted by Goetz and
Field~\cite{goetz12fdefenders} to formalize defender (default) methods in
Java.
In their formalization, classes and interfaces can have only one method \Q@m()@ without arguments, so as to simplify method overloading and renaming.
Our work expands and generalizes the situation to support multiple methods with some arguments inside interfaces, in which case the methods that \mixin generates are better modelled. Meanwhile, features like multiple inheritance of interfaces and reabstraction of default methods are also preserved in our formalization. Furthermore, one advantage of the \Q@of@ method provided by \mixin is that it's generated as a static method, considered as a clean way without affecting its heirs. It is indeed supported since static methods are included in our formalization.
\bruno{explain why having multiple methods is significantly
  more challenging.}
%Our code generation generates several methods that may
%interacts with each other and methods defined by user. Thus implementing and
%formalizing multiple methods inside interfaces adds complexity greatly.
\marco{I do not see this as a good explanation, I think we may just remove the `one method limitation discussion'. Is their work modelling interactions between abstract and default methods? like making a default method abstract again?}
% As an evidence of the attention and care present in our formalization work,
% while double-checking the behaviour of Java in side cases we have discovered a
% likely bug in the current \texttt{javac}.\marco{refer to before when we explain
%   the issue.}
